%------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{setspace}
\usepackage{cooltooltips}% http://ctan.org/pkg/cooltooltips
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{kpfonts}  % \fontfamily{kpfonts} by default
% \usepackage{CormorantGaramond}
\usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\setlength{\footskip}{4.08003pt}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\blueLink}[2]{
  \href{#1}{\color{blue}\textbf{\underline{#2}}}
}

\newcommand{\textHover}[2]{
  \cooltooltip[1 1 1]{}{}{}{#2}{#1}
}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://mostafa-qusit.com/}{\Large Mostafa Qusit}} & Email : \href{mailto:mostafahmedqusit@gmail.com}{mostafahmedqusit@gmail.com}\\
%   \href{http://mostafa-qusit.com/}{http://www.mostafa-qusit.com} & Mobile : +2-01151173660 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Mostafa Ahmed Mahmoud Mohamed Qusit} \\ \vspace{1pt}
    \small
    \begin{spacing}{1.25}
      \textbf{01151173660} $|$
      \blueLink{mailto:mostafahmedqusit@gmail.com}{mostafahmedqusit@gmail.com} $|$
      \blueLink{https://linkedin.com/in/mostafa-qusit}{linkedin.com/in/mostafa-qusit} $|$
      \blueLink{https://github.com/MostafaQusit}{github.com/MostafaQusit}
    \end{spacing}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Faculty of Engineering - Ain Shams University}{Abdo Pasha, Cairo}
      {Bachelor of Science (BSc) in Mechanical Engineering – Mechatronics Engineering Program}{Sep. 2018 -- July 2023}
      \resumeItemListStart
        \resumeItem{GPA: 3.43 (9th on my class)}
        \resumeItem{Graduation Project GPA: 4.0 (A+)}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {B1 Aircraft Maintenance Scheduling Engineer}{May 2024 -- Present}
      {EGYPTAIR MAINTENANCE AND ENGINEERING - CAMO - Scheduling Dep.}{Cairo International Airport, Cairo}
      \resumeItemListStart
      \resumeItem{\textbf{Bill of Work (BOW):}\\
      - Prepared and managed comprehensive BOWs to ensure aircraft airworthiness and compliance with the Aircraft Maintenance Program (MP), service bulletins, and modifications.\\
      - Scheduled MP tasks in alignment with compliance deadlines, flight hours (FH), and flight cycles (FC).}
     
      \resumeItem{\textbf{Engineering Orders (EO):}\\
      - Received, evaluated, and scheduled EOs based on compliance deadlines, FH, and FC. \\
      - Ensured resources, materials, and man-hours were allocated effectively for EO execution.}
     
      \resumeItem{\textbf{Time-Controlled Items (TCI):}\\
      - Reviewed TCI lists to identify compliance due dates and scheduled tasks accordingly. \\
      - Monitored TCI progress and resolved delays to ensure timely completion.}
     
      \resumeItem{\textbf{Deferred Defects:}\\
      - Reviewed, prioritized, and scheduled deferred defects for resolution based on resources and compliance deadlines. \\
      - Coordinated with relevant departments to facilitate closure and follow-up.}
     
      \resumeItem{\textbf{Open Items:}\\
      - Scheduled and tracked tasks from Open Items Lists to meet compliance requirements. \\
      - Ensured timely resolution of all open items and prevented delays.}
      \resumeItemListEnd
      
    % -----------Multiple Positions Heading-----------
    %    \resumeSubSubheading
    %     {Software Engineer I}{Oct 2014 - Sep 2016}
    %     \resumeItemListStart
    %        \resumeItem{Apache Beam}
    %          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
    %     \resumeItemListEnd
    %    \resumeSubHeadingListEnd
    %-------------------------------------------

    \resumeSubheading
      {IT Programming Instructor}{Sep. 2023 -- May 2024}
      {NASS Academy - WE School of Applied Technology - 1st Secondary Grade}{Nasr City, Cairo}
      \resumeItemListStart
        \resumeItem{Delivered engaging and interactive 4 main topics in \textbf{IT-related subjects:}
          \emph{(\textHover{Computer Architecture}{introduction to computer and computer component.},
          \textHover{Computer Networks}{network types, topologies and devices, OSI Model, IPv4, etc.. (Basics CCNA).}, 
          \textHover{Intro. to computer programming and Python}{programming concepts, mBlock, and Python Basics.},
          \textHover{IT Systems in Organization}{IT infrastructure, data and information, IT threats, ethics and policies.})}}
        \resumeItem{Integrated technology tools into teaching, including smart boards and Google Classroom, to enhance the learning experience.}
        \resumeItem{Fostered practical skills through hands-on activities and real-world projects.}
        \resumeItem{Assessed student performance using diverse evaluation methods, including quizzes, exams, and reports for international accreditation.}
        \resumeItem{Contributed to curriculum development by creating quizzes, question banks, and participating in grading process.}
        \resumeItem{Collaborated with colleagues to share best practices, refine teaching methods, and improve overall instruction quality.}
        \resumeItem{Enhanced teaching and presentation skills by adapting to dynamic classroom needs and implementing innovative approaches.}
      \resumeItemListEnd

    \resumeSubheading
      {Embedded Software Engineer}{Aug. 2022 -- Sep. 2022}
      {MASAR ELECTRIC - Embedded Systems Department}{Abdeen, Cairo}
      \resumeItemListStart
      \resumeItem{Developed and contributed to multiple embedded and automation projects, including:\\
      - Cooler Unit Project and Concrete Project, delivering efficient and reliable solutions.}
     
      \resumeItem{Implemented and integrated Human-Machine Interface (HMI) systems using DWIN DGUS II Touch Screen: \\
      - Designed and developed both front-end and back-end functionalities to enable seamless communication with microcontrollers.}
     
      \resumeItem{Engineered approximately 15 AVR embedded drivers across various layers:\\
      - MCAL Layer: Developed drivers for DIO, ADC, PWM, SPI, I2C, and other hardware abstractions. \\
      - HCL Layer: Created drivers for higher-level modules, including Keypad, LCD, and SD-Card integration.}
      \resumeItemListEnd

    \resumeSubheading
      {Maintenance Engineer (Intern)}{Aug. 2021 -- Sep. 2021}
      {Royal Company for Ceramics Industry - Electrical Maintenance in sorting and packaging Dep.}{El Obour City, Cairo}
      \resumeItemListStart
        \resumeItem{followed up the production line in detail, especially the sorting and packing part.}
        \resumeItem{Benefited and learned during maintenance operations, and understand potential and common faults, whether electrical, mechanical repairs, etc...}
      \resumeItemListEnd

  \resumeSubHeadingListEnd




%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
        {\textbf{\href{https://github.com/MostafaQusit/Simple-Online-Store}{Simple Online Store}} $|$ \emph{GitHub, VS Code, HTML, CSS, JavaScript, React}}{Sep 2023 -- Oct 2023}
        \resumeItemListStart
          \resumeItem{Designed and developed a simple online store using Front-End Framework called \textbf{React} (JavaScript-based).}
          \resumeItem{Implemented features like product listing, product details.}
          \resumeItem{Utilized React Hooks for state management and API calls.}
        \resumeItemListEnd

      \resumeProjectHeading
        {\textbf{\href{https://github.com/MostafaQusit/MAHR-GraduationProject}{M.A.H.R}} $|$ \emph{PlatfromIO IDE, ESP, ESP-NOW, IOT, Wi-Fi, Arduino, Python}}{Oct 2022 -- July 2023}
        \resumeItemListStart
          \resumeItem{A \textbf{M}ulti-function \textbf{A}utonomous \textbf{H}ousehold \textbf{R}obot, capable of navigating through the house on its own.}
          \resumeItem{\textbf{Autonomous Navigation:}\\
          - The robot is designed to navigate autonomously through the house, ensuring efficient movement and obstacle avoidance.\\
          - Motion Analysis: Implemented using MATLAB and Simulink to ensure stability during planar motion, enabling the robot to maintain balance while overcoming small obstacles.}
          
          \resumeItem{\textbf{Mechanical Design:}\\
          - Developed an optimized multi-material mechanical model using SOLIDWORKS to create a lightweight, yet rigid chassis (weighing 35 kg).}
          
          \resumeItem{\textbf{Manipulation System:}\\
          - Equipped with a 5 Degrees of Freedom (DOF) manipulator arm featuring: (Belt transmission mechanisms, Gear ratios, Differential wrist joint, Semi-soft gripper that adapts to the geometry of objects being grabbed)}
          
          \resumeItem{\textbf{Communication Capabilities:}\\
          - Integrated 4 communication methods, including: (USART, Wi-Fi, Bluetooth, ESP-NOW (for ESP boards only))\\
          - SIM800L Module: Allows the robot to make calls and send messages.\\
          - MP3 Module: Provides voice comments based on the robot's state for enhanced interaction.}
          
          \resumeItem{\textbf{Control and Feedback:}\\
          Control via a custom app and PS4 controller for manual or autonomous operation.\\
          Features live-streaming via a 2MP camera for real-time feedback and monitoring.}
          
          \resumeItem{\textbf{Custom PCB Design:}\\
          - The robot includes 2 custom-designed PCB boards for efficient management and integration of all components.}
          
          \resumeItem{\textbf{Software Architecture:}\\
          - Low-Level Control: Handled by ESP32 boards using PlatfromIO IDE (Application layer). *My Contribution*\\
          - High-Level Control: Managed by Raspberry Pi 4B using the Robot Operating System (ROS).}
        \resumeItemListEnd

      \resumeProjectHeading
        {\textbf{Service Towers Distribution - Optimization Problem} $|$ \emph{Jupyter, Python}}{Feb 2023 -- Jun 2023}
        \resumeItemListStart
          \resumeItem{aimed to distribute service towers over a defined map, with certain constraints, using Python programming.}
          \resumeItem{5 optimization techniques were used, Simulated Annealing \textbf{SA}, Genetics Algorithm \textbf{GA}, Particle Swarm Optimization \textbf{PSO}, Ant colony Optimization \textbf{ACO}, Grey Wolf Optimization \textbf{GWO}.}
        \resumeItemListEnd
      
      \resumeProjectHeading
        {\textbf{Machine Learning Model} $|$ \emph{Jupyter, Python, OpenCV, TensorFlow}}{Oct 2022 -- Feb 2023}
        \resumeItemListStart
          \resumeItem{developed a ML classifier the \textbf{CIFAR100} dataset using the OpenCV library and Python programming:\\
          Part 1: used \textbf{HOG} as Feature Extraction and (\textbf{KNN}, \textbf{K-means}, and \textbf{SVM}) as [3]Classifiers.\\
          Part 2: used \textbf{CNN} as Feature Extraction and Classifier.\\
          Part 3: used \textbf{CNN} as Feature Extraction and Classifier with the pre-trained model \textbf{VGG16} as a base model.}
        \resumeItemListEnd
          
      \resumeProjectHeading
        {\textbf{Mathematical Optimization Problem} $|$ \emph{Jupyter, Python, NumPy, SymPy, SciPy}}{Oct 2022 -- Feb 2023}
        \resumeItemListStart
          \resumeItem{aimed to optimized a complex mathematical equation using Python programming.}
          \resumeItem{3 optimizations methods were implemented: (Gradient Descent, Newton Raphson, and Steepest Descent).}
        \resumeItemListEnd

      \resumeProjectHeading
      {\textbf{Furuta Pendulum - Hybrid Control Problem} $|$ \emph{Matlab, Simulink , Arduino}}{Oct 2022 -- Feb 2023}
      \resumeItemListStart
        \resumeItem{Aimed to reach stability of the inverted pendlum through the rotation of the system's driven base.}
        \resumeItem{2 Control techniques were used, linear-Quadratic Regulator Controller \textbf{(LQR)}, Proportional–Integral–Derivative Controller\textbf{(PID)}}
      \resumeItemListEnd  

      \resumeProjectHeading
        {\textbf{\href{https://github.com/MostafaQusit/CNC-Plotting-Machine}{3-Axis Parallel CNC Plotting Machine}} $|$ \emph{Arduino}}{Mar 2022 -- Jun 2022}
        \resumeItemListStart
          \resumeItem{A CNC M/C capable of drawing 2D pictures and writing using a pen (3 DOF).}
          \resumeItem{Was implemented using 2 different control algorithms: open loop using 2 stepper motors and closed loop using 2 PID-controlled DC motors and 2 encoders for the feedback and servo for Vertical motion(Pen up and down).}
          \resumeItem{An app was made to provide the CNC with the required text to be written.}
        \resumeItemListEnd

      \resumeProjectHeading
        {\textbf{\href{https://github.com/MostafaQusit/RRR-Serial-Robotic-Arm}{RRR Serial Robotic Arm}} $|$ \emph{Arduino}}{April 2022 -- Jun 2022}
        \resumeItemListStart
          \resumeItem{An RRR (3 Revolute joint) serial robot capable of drawing numbers.}
          \resumeItem{Trajectory planning was implemented to achieve concise positioning, and Inverse kinematics were used to get the required angle of each joint.}
          \resumeItem{3 servo motors were considered as an actuator with a built-in feedback element to optimize the control process.}
        \resumeItemListEnd
      
        \resumeProjectHeading
        {\textbf{Production Line and Storage Control} $|$ \emph{Factory I/O, TIA Portal}} {Nov. 2021--Dec. 2021}
        \resumeItemListStart
          \resumeItem{Designed and Implemented the Ladder Control Diagram of the Automation of the Production Line.}
        \resumeItemListEnd 
    \resumeSubHeadingListEnd
% \pagebreak

%-----------COURSES------------
\section{Courses \& Trainings}
  \resumeSubHeadingListStart
    \resumeProjectHeading
    {\textbf{\href{https://training.egyptair.com/crm/Catalog/9300}{Basic complementary Course for A\&C Engineers}} $|$ \emph{EGYPTAIR TRAINING ACADEMY}}{Feb 2025}
    \resumeItemListStart
      \resumeItem{Phase (1): Electrical Systems}
      \resumeItem{Phase (2): Avionics Systems}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{\href{https://training.egyptair.com/crm/Catalog/45100}{Aviation Regulation Course for Engineers}} $|$ \emph{EGYPTAIR TRAINING ACADEMY}}{Jan 2025}
    \resumeItemListStart
      \resumeItem{Egyptian Civil Aviation Regulations (ECARs) by Egyptian Civil Aviation Authority (ECAA).}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{AMOS Software training for Scheduling/Planning Engineers} $|$ \emph{EGYPTAIR M\&E}}{Dec 2024 - Present}
    \resumeItemListStart
      \resumeItem{Theoretical and Practical training with real-world application at work.}
    \resumeItemListEnd
    
    \resumeProjectHeading
      {\textbf{\href{https://training.egyptair.com/CRM/Catalog/45200}{Basic Indoctrination for Aero./Mech. Engineers}} $|$ \emph{EGYPTAIR TRAINING ACADEMY}}{Aug 2024 -- Nov 2024}
      \resumeItemListStart
        \resumeItem{Phase (1): Inspection Procedures}
        \resumeItem{Phase (2): Power Sources \& Avionics}
        \resumeItem{Phase (3): Airframe Systems (I)}
        \resumeItem{Phase (4): Airframe Systems (II)}
        \resumeItem{Phase (5): Engine Systems (I)}
        \resumeItem{Phase (6): Engine Systems (II)}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{\href{https://training.egyptair.com/CRM/Catalog/42400}{Pre Basic for Mechanical Engineers}} $|$ \emph{EGYPTAIR TRAINING ACADEMY}}{July 2024 -- Aug 2024}
      \resumeItemListStart
        \resumeItem{Aerodynamics}
        \resumeItem{Aircraft Performance}
        \resumeItem{Engine Performance}
        \resumeItem{Digital Techniques}
        \resumeItem{Weight and Balance}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{\href{https://training.egyptair.com/CRM/Catalog/55200}{Aircraft Maintenance Planning \& Scheduling For Engineers}} $|$ \emph{AACO Training Center-RTC}}{June 2024}
    
    \resumeProjectHeading
      {\textbf{\href{https://docs.google.com/document/d/1X7FlRX-Re-GHMI3wuXc9e37jJEGl_DlxNb-6NCMlmgo/edit?usp=sharing}{Embedded Systems}} $|$ \emph{Eng. Ahmed Abd El-Ghafar}}{July 2024 -- Present}
      \resumeItemListStart
        \resumeItem{C Programming, Data Structure and algorithms.}
        \resumeItem{Microcontroller Interfacing.}
        \resumeItem{Automotive Protocols (CAN, LIN), AUTOSAR and MISRA C.}
        \resumeItem{Automotive, Bootloader and ARM Cortex M4 Architecture.}
        \resumeItem{Real Time Operating System (RTOS)}
      \resumeItemListEnd
    
    \resumeProjectHeading
      {\textbf{E-Waste Refurbishment Curriculum Train-OF-Trainers} $|$ \emph{Electronics Research Institute}}{Feb 2024}

    \resumeProjectHeading
      {\textbf{Competency-based learning Training} $|$ \emph{Ministry of Education and Technical Education}}{Dec 2023}

    \resumeProjectHeading
      {\textbf{Full-Stack for beginners} $|$ \emph{NASS Academy - WE School}}{Sep 2023}
      \resumeItemListStart
        \resumeItem{Front-End: HTML, CSS/Bootstrap, JavaScript/React.}
        \resumeItem{Back-End: Node.js, Express.js, MySQL.}
      \resumeItemListEnd
    
    \resumeProjectHeading
      {\textbf{\href{https://www.coursera.org/projects/create-financial-statement-using-microsoft-excel}{Create a Financial Statement using Microsoft Excel}} $|$ \emph{Coursera}}{Sep 2023}

    \resumeProjectHeading
      {\textbf{\href{https://matlabacademy.mathworks.com/details/matlab-onramp/gettingstarted}{MATLAB Onramp}} $|$ \emph{MathWorks}}{Oct 2022}
    
    \resumeProjectHeading
      {\textbf{\href{https://matlabacademy.mathworks.com/details/simulink-onramp/simulink}{Simulink Onramp}} $|$ \emph{MathWorks}}{Oct 2022}

    \resumeProjectHeading
      {\textbf{\href{https://drive.google.com/drive/folders/1gKIz-PYpO2zrjnvkzoYVhijYoGJP7P9j?usp=sharing}{Basic programming and operating CNC Milling centers using Fanuc Oi}} $|$ \emph{AOI Academy}}{Oct 2021}
      \resumeItemListStart
        \resumeItem{learn G-code \& M-code programming.}
        \resumeItem{program simple contour milling and drilling cycles.}
        \resumeSubItem{program, operate and set up 3-axis CNC Milling M/C using Fanuc Oi.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Fundamental Embedded Systems} $|$ \emph{Eng. Hussien Hossam}}{Feb 2021 -- Sep 2021}
      \resumeItemListStart
        \resumeItem{C Programming Language, Data Structure Algorithms.}
        \resumeItem{Embedded Systems by AVR Microcontrollers.}
      \resumeItemListEnd
  
    \resumeProjectHeading
      {\textbf{Building Arduino robots and devices} $|$ \emph{Coursera}}{Sep 2020}
      
    \resumeProjectHeading
      {\textbf{Introduction to Programming with MATLAB (level 1/3)} $|$ \emph{Coursera}}{Sep 2020}
    
    \resumeProjectHeading
      {\textbf{Getting Started with Python (Level 1/5)} $|$ \emph{Coursera}}{Sep 2020}  
    
    \resumeProjectHeading
      {\textbf{Supply Chain} $|$ \emph{IDT Student Activity}}{April 2020}
      \resumeItemListStart[label={}]
        \resumeItem{Lean Manufacturing, 6-sigma, Quality, etc...}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Skills}
  \resumeItemListStart
    \resumeItem{\textbf{Computer Applications:} \\
        - MS Office (Excel, PowerPoint, Word) \\
        - Aviation Maintenance \& Operational Systems (AMOS)}
    \resumeItem{\textbf{Mechanical Design:} SOLIDWORKS, Inventor, AutoCAD}
    \resumeItem{\textbf{Languages:} Arabic (Native), English (Professional)}
    
    \resumeItem{
      \textbf{Programming:} \\
        \textbf{- Languages:} Python, C/C++, SQL (MySQL), JavaScript, HTML/CSS, MATLAB/Simulink, G-Code \\
        \textbf{- Frameworks:} Arduino, Bootstrap, React, Node.js, Express \\
        \textbf{- Tools:} Git, GitHub, VS Code, PyCharm, IAR, Microchip/Atmel, PlatfromIO IDE, Jupyter, Arduino IDE \\
        \textbf{- Boards:} AVR, ESP32, STM32, ARM Cortex M4 \\
        \textbf{- Libraries:} Python(NumPy, SymPy, SciPy, Pandas, Matplotlib, OpenCV, TensorFlow)
    }
    \resumeItem{
      \textbf{Soft Skills:} Teamwork, Communication, Problem Solving, Time Management, Adaptability, Public Speaking.
    }
  \resumeItemListEnd


%-------------------------------------------
\end{document}